Historical Supply of Residual Biomass from Timber Harvest in West-central Alberta, Canada

### 2021-10-05 analysis/manuscript.Rmd
stuff

---
title: "Historical supply of timber harvest residues in west-central Alberta"
author:
- Glen W Armstrong^[Department of Renewable Resources, University of Alberta]
- Jay Anderson^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Alex McPhee^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
date: "2021-09-10"
output:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
  word_document:
  html_document:
    df_print: paged
bibliography: historicalResidueSupply.bib
---

@@

```{r libraries, echo=FALSE, message=FALSE}
#setwd("/home/gwa/Work/historical-residue/Analysis")
#setwd("g:/Shared drives/FES_Data_Sharing (Forestry)/Manuscripts/Historical Residue Supply/Analysis")

library(tidyverse)
library(ggthemes)
library(gridExtra)
library(viridis)
library(skimr)
library(scales)
library(DescTools)
library(zoo)
library(ezknitr)
#ezknit(file="analysis/manuscript.Rmd", out_dir="output", fig_dir="myfigs")
```

@@

@@

```{r read data files, echo=FALSE}
t <- read.csv(file = '../data/township_merchantable_volume.csv')
twp_merch_vol <- t %>% select(c(TRM,mean_merch_volume)) 
twp_merch_vol$adj_vol <- twp_merch_vol$mean_merch_volume * merch_vol_adj_factor
twp_merch_vol$residue_odmt <- twp_merch_vol$adj_vol * odmt_adj_factor

@@

```{r supply curves, echo=FALSE, warning=FALSE, fig.cap="Residue supply (cycle time) curves by location.  Each curve represents one year.  The red curve is for 2009, which was the year of median harvest volume."}

@@

```{r more supply curves, echo=FALSE, warning=FALSE, fig.cap="Residue supply (delivered cost) curves by location.  Each curve represents one year.  The red curve is for 2009, which was the year of median harvest volume."}
ggplot(data=cum.odmt, aes(x=residue.cumsum,y=residueCost,group=year,colour=as.factor(year))) +
  labs(x = "cumulative residue (1000 odmt)") +
  labs(y = "marginal cost ($/odmt)") +
  geom_line() +
  scale_colour_manual(values=c("Grey","Grey","Grey","Grey","Grey","Grey","Grey",
                               "Grey","Grey","Grey","Grey","Grey","Grey","Grey",
                               "Grey","Grey","Grey","Grey","Grey","Red","Grey",
                               "Grey","Grey","Grey","Grey","Grey","Red")) +
#  scale_colour_viridis(discrete = TRUE) +
  geom_line(data=cum.odmt[cum.odmt$year==2009,],aes(x=residue.cumsum,y=residueCost, colour="Red"))+
  theme(legend.position = "none") +
  facet_grid(cols=vars(location)) +
  scale_x_continuous(limits=c(0,800000),labels = label_number(scale = 1/1000)) +
  scale_y_continuous(limits=c(50,175)) 
```

@@

Dennis Gray.  Future Energy Systems.

>>>>

---
title: "Historical Supply of Residual Biomass from Timber Harvest in West-central Alberta, Canada"
author:
- Glen W. Armstrong^[Department of Renewable Resources, University of Alberta]
- Jay A. Anderson^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
- Alex W. McPhee^[Department of Resource Economics and Environmental Sociology, University
  of Alberta]
date: "`r format(Sys.time(), '%Y-%m-%d')`"
#date: "2021-10-05"
output:
  html_document:
    df_print: paged
  word_document:
  pdf_document:
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
csl: canadian-journal-of-forest-research
#csl: biomass-and-bioenergy
bibliography: historicalResidueSupply.bib
---

@@

```{r libraries, echo=FALSE, message=FALSE}
#setwd("/home/gwa/Work/historical-residue/Analysis")
#setwd("g:/Shared drives/FES_Data_Sharing (Forestry)/Manuscripts/Historical ResidueSupply/Analysis")
setwd("/mnt/chromeos/GoogleDrive/SharedDrives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")
library(tidyverse)
library(ggthemes)
library(gridExtra)
library(viridis)
library(skimr)
library(scales)
library(DescTools)
library(zoo)
library(ezknitr)
#ezknit(file="analysis/manuscript.Rmd", out_dir="output", fig_dir="myfigs")
```

@@

@Boudewyn2007

@@

```{r read_data_files, echo=FALSE}
t <- read.csv(file = '../data/township_merchantable_volume.csv')
twp_merch_vol <- t %>% select(c(TRM,mean_merch_volume)) 
twp_merch_vol$adj_vol <- twp_merch_vol$mean_merch_volume * merch_vol_adj_factor
twp_merch_vol$residue_odmt <- twp_merch_vol$adj_vol * odmt_adj_factor

@@

```{r supply_curves, echo=FALSE, warning=FALSE, fig.cap="Residue supply (cycle time) curves by location.  Each curve represents one year.  The red curve is for 2009, which was the year of median harvest volume."}

@@

```{r more_supply_curves, echo=FALSE, warning=FALSE, fig.cap="Residue supply (delivered cost) curves by location.  Each curve represents one year.  The red curve is for 2009, which was the year of median harvest volume."}
ggplot(data=cum.odmt, aes(x=residue.cumsum,y=residueCost,group=year,colour=as.factor(year))) +
  labs(x = "cumulative residue (1000 odmt)") +
  labs(y = "marginal cost ($/odmt)") +
  geom_line() +
  scale_colour_manual(values=c("Grey","Grey","Grey","Grey","Grey","Grey","Grey",
                               "Grey","Grey","Grey","Grey","Grey","Grey","Grey",
                               "Grey","Grey","Grey","Grey","Grey","Red","Grey",
                               "Grey","Grey","Grey","Grey","Grey","Red")) +
#  scale_colour_viridis(discrete = TRUE) +
  geom_line(data=cum.odmt[cum.odmt$year==2009,],aes(x=residue.cumsum,y=residueCost, colour="Red"))+
  theme(legend.position = "none") +
  facet_grid(cols=vars(location)) +
  scale_x_continuous(limits=c(0,800000),labels = label_number(scale = 1/1000)) +
  scale_y_continuous(limits=c(50,175)) 
```

@@

Dennis Gray contributed to data collection.  Funding was provided by Future Energy Systems, University of Alberta.
